### 2023-02-14 tables/fairness/fvgm/sanity_check.tex
short captions

	\caption{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on logistic regression classifier.}
	\label{fairness_fvgm_fig:synthetic_results}
\end{figure}

@@

	\caption{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on SVM classifier.}
	\label{fairness_fvgm_fig:synthetic_results_SVM}
\end{figure}

>>>>

	\caption[Accuracy of {\fvgm} on logistic regression classifier]{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on logistic regression classifier.}
	\label{fairness_fvgm_fig:synthetic_results}
\end{figure}

@@

	\caption[Accuracy of {\fvgm} on SVM classifier]{
		Measuring accuracy of different fairness verifiers for Example~\ref{fvgm_example:intro} on SVM classifier.}
	\label{fairness_fvgm_fig:synthetic_results_SVM}
\end{figure}
